---
title: "AdjCausDisc"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{AdjCausDisc}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(AdjCausDisc)
```

# AdjCausDisc

The main goal of AdjCausDisc is to use the input of an Adjacency Matrix that represents the structure of the Directed Acyclic Graph (DAG) and the dataset Y where the DAG represents the relationship between each of the entries of Y.



However, what exactly is a Directed Acyclic Graph? 

## Directed Acyclic Graphs

A Directed Acyclic Graph is a conceptual representation of causal relationship between data points. For example consider a dataset Y = (Y1, Y2, Y3), where Y1 represents number of cigarettes smoked, Y2 represents the number of hours worked in a factory, and Y3 represents number of cancer cells in the lungs. 

```{r}
Adjacency_matrix = matrix(nrow=3,ncol=3,0)
Adjacency_matrix[,1]=c(0,1,1)
Adjacency_matrix[,2]=c(0,0,1)
Adjacency_matrix[,3]=c(0,0,0)


AdjDAG(Adjacency_matrix)
```
